\section{Experience}

\begin{entrylist}
%-----------------------------------------------
\entry
{2023}
{\textsc{Biologics Analytical Operations}, Gilead Sciences}
{Oceanside, CA}
{\emph{Summer Intern} \\
Utilized data science to streamline workflows and enhance productivity for end users.
\begin{itemize}
\item Conducted data wrangling and visualization, facilitating insights from high-dimensional data.
\item Engineered a real-time monitoring Plotly Dashboard for mass spectrometer instrument status.
\item Automated peptide mapping lab notebook submissions, streamlining workflow efficiency.
\item Enhanced Quality by Design Database (QbD-DB) workflow, optimizing user experience.
\end{itemize}}
%-----------------------------------------------
\entry
{2022}
{\textsc{Biologics Analytical Operations}, Gilead Sciences}
{Oceanside, CA}
{\emph{Summer Intern} \\
 Pioneered the establishment of a Quality by Design Database (QbD-DB) within the Benching lab notebook ecosystem, orchestrating data design, curation, and relational connectivity for streamlined workflows. 
\begin{itemize}
\item Optimized data retrieval, implemented efficient data upload processes, and facilitated data analysis workflows. 
\item Leveraged SQL for data aggregation within the warehouse, improving data accessibility. 
\item Successfully launched QbD-DB and provided comprehensive end-user training. 
\item Conducted data wrangling and visualization for complex high-dimensional data sets.
\end{itemize}}
%----------------------------------------------
\entry
{2016--2023}
{\textsc{Shimon Weiss Lab}, UCLA}
{Los Angeles, CA}
{\emph{Graduate Student Researcher}\\
Conducted pioneering research in biophysics, specializing in the development of high-throughput single-molecule Fluorescence Resonance Energy Transfer (smFRET) spectroscopy techniques to investigate transcription initiation by RNA Polymerase.
\begin{itemize}
\item Designed and executed smFRET assays using a cutting-edge high-throughput confocal microscope, unveiling structural dynamics and kinetics of transcription by bacterial RNA polymerase.
\item Spearheaded the development of smFRET assays to probe structural and mechanistic aspects of bacterial transcription by RNA polymerase and viral transcription/replication by RNA-dependent RNA polymerase.
\item Orchestrated sample preparation, including the design and construction of a plasmid library for protein labeling, conducted protein and oligonucleotide purification via gel electrophoresis, and conducted cell and protein preparations.
\item Innovatively designed smFRET assays, encompassing oligonucleotide construct design, FRET pair design, labeling strategies, and predicted FRET efficiencies using cutting-edge software.
\item Performed advanced data analysis, including statistical analysis of large single-photon datasets, utilizing Python to extract meaningful insights.
\end{itemize}}
%-----------------------------------------------
\entry
{2016}
{\textsc{Gelbart \& Knobler Lab}, UCLA}
{Los Angeles, CA}
{\emph{Graduate Student Researcher}\\
Conducted a focused summer rotation with a research emphasis on the physical chemistry of RNA virus self-assembly.
\begin{itemize}
\item Employed a theory-driven approach to investigate the physical properties of RNA viruses and virus-like proteins (VLPs), advancing the understanding of their fundamental characteristics.
\item Characterized VLP-enveloped viral RNA through tunneling electron microscopy.
\end{itemize}}
%-----------------------------------------------
\entry
{2015-2016}
{\textsc{Yildiz Lab}, UC Berkeley}
{Berkeley, CA}
{\emph{Undergraduate Student Researcher}\\
Engaged in groundbreaking research utilizing Total Internal Reflection Fluorescence (TIRF) microscopy to investigate the behavior of kinesin motor proteins at the super-resolution level.
\begin{itemize}
\item Employed TIRF microscopy techniques to elucidate the influence of intramolecular strain on the coordination of kinesin motor domain stepping patterns, advancing the understanding of motor protein mechanics.
\item Spearheaded the optimization of small custom quantum dots for high-resolution single-molecule imaging, enabling precise tracking of motor proteins.
\item Conducted dual-color quantum dot surface immobilized motility assays, facilitating single-molecule tracking and colocalization studies of kinesin motor domains using TIRF microscopy.
\item Optimized and characterized bioconjugation techniques for labeling kinesin with fluorescent probes.
\end{itemize}}
%-----------------------------------------------
\entry
{2015}
{\textsc{Molecular Foundry}, Lawrence Berkeley National Lab}
{Berkeley, CA}
{\emph{Undergraduate Student Researcher}\\
Contributed to a dynamic summer internship focused on the passivation and conjugation of upconverting nanocrystals and quantum dots.
\begin{itemize}
\item Passivated the surfaces of upconverting nanocrystals and quantum dots using a novel amphiphilic peptoid wrapping, enhancing their stability and functionality for subsequent applications.
\item Pioneered a method for precise and controlled modification of peptoid-conjugated upconverting nanoparticle surfaces, enabling targeted bioconjugation and expanded versatility.
\item Proficiently employed a range of characterization techniques, including UV-Vis spectroscopy, MALDI mass spectrometry, dynamic light scattering (DLS), fast protein liquid chromatography (FPLC), and fluorimetry, to comprehensively analyze and validate experimental outcomes.
\end{itemize}}
\end{entrylist}

